Improving Software Maintainability through Automated Refactoring of Duplicate Code

### 2020-01-11 ecoop/paper.tex
Threats to validity

\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{float}

@@

\usepackage{chngpage}

\usepackage{courier}

\usepackage{etoolbox}
\AtBeginEnvironment{quote}{\singlespacing\footnotesize\ttfamily}

@@

\begin{adjustwidth}{-0.5in}{-0.5in}% adjust the L and R margins by 1 inch
\begin{minipage}{\linewidth}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
package com.sb.game;

@@

	public String concatTen(String x) {
|\highlightYellow|		x = x + 10; // String concatenation
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
%\caption{Example of textually equal code fragments that differ in functionality.}
%\label{fig:type1}
%\end{figure*}
\end{minipage}
\end{adjustwidth}

@@

The full commit message for the refactoring example displayed in Fig.~\ref{fig:cr_refactoring} is as follows:
\begin{quote}
CloneRefactor refactored a clone class with 2 clone instances. For the common code we created a new method and named this method “cloneRefactor0". These clone instances have a Same Method relation with each other. The newly created method has been placed in ISODateTimeFormat. Each duplicated fragment has been replaced with a call to this method.
\\ \\
== System Quality Metrics == \\
Total Cyclomatic Complexity increased by 1 from 6,994 to 6,995.\\
Total Unit Interface Size increased by 1 from 3,715 to 3,716.\\
Total Unit Line Size increased by 1 from 23,024 to 23,025.\\
Total Unit Token Size decreased by 2 from 153,190 to 153,188.\\
Total Nodes decreased by 1 from 18,866 to 18,865.\\
\\
Duplicated Nodes decreased by 6 from 502 to 496.\\
Duplicated Tokens decreased by 42 from 5,064 to 5,022.\\
Duplicated Lines decreased by 6 from 504 to 498.\\
\\
== Risk Profiles ==\\
Unit Complexity\\
Created a new method with a low risk Unit Complexity of 1.\\
Removing duplicate blocks changed 1 method.\\
The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 8 to 8 Unit Complexity. This did not influence the risk category of this method, it is still low risk.\\
\\
Line Volume\\
Created a new method with a low risk Line Volume of 5.\\
Removing duplicate blocks changed 1 method.\\
The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 47 to 39 Line Volume. This did not influence the risk category of this method, it is still high risk.\\
\\
Token Volume\\
Created a new method with a low risk Token Volume of 30.\\
Removing duplicate blocks changed 1 method.\\
The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 303 to 271 Token Volume. This increased the risk category of this method from high to moderate.\\
\\
The new method has a low risk Unit Interface Size of 1.\\
\\
Duplication went from 2.66\% to 2.63\%. This did not influence the risk category of the duplication in this codebase, it is still low risk.
\end{quote}

@@

>>>>

\usepackage[table]{xcolor}
\usepackage{graphicx}
\usepackage{float}

@@

\usepackage{chngpage}
\usepackage{courier}
\usepackage{etoolbox}
\AtBeginEnvironment{quote}{\footnotesize\ttfamily}

@@

\begin{figure*}
\begin{adjustwidth}{-0.5in}{-0.5in}% adjust the L and R margins by 1 inch
\begin{minipage}{\linewidth}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
package com.sb.game;

@@

	public String concatTen(String x) {
|\highlightYellow|		x = x + 10; // String concatenation
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
\end{minipage}
\end{adjustwidth}
\caption{Example of textually equal code fragments that differ in functionality.}
\label{fig:type1}
\end{figure*}

@@

The full commit message for the refactoring example displayed in Fig.~\ref{fig:cr_refactoring} is as follows:
\begin{quote}
CR refactored a clone class with 2 clone instances. For the common code we created a new method and named this method “refactoredClone0". These clone instances have a Same Method relation with each other. The newly created method has been placed in ISODateTimeFormat. Each duplicated fragment has been replaced with a call to this method.
\\ \\
== System Quality Metrics == \\
Total Cyclomatic Complexity increased by 1 from 6,994 to 6,995.\\
Total Unit Interface Size increased by 1 from 3,715 to 3,716.\\
Total Unit Line Size increased by 1 from 23,024 to 23,025.\\
Total Unit Token Size decreased by 2 from 153,190 to 153,188.\\
Total Nodes decreased by 1 from 18,866 to 18,865.\\
\\
Duplicated Nodes decreased by 6 from 502 to 496.\\
Duplicated Tokens decreased by 42 from 5,064 to 5,022.\\
Duplicated Lines decreased by 6 from 504 to 498.\\
\\
== Risk Profiles ==\\
Unit Complexity\\
Created a new method with a low risk Unit Complexity of 1.\\
Removing duplicate blocks changed 1 method.\\
The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 8 to 8 Unit Complexity. This did not influence the risk category of this method, it is still low risk.\\
\\
Line Volume\\
Created a new method with a low risk Line Volume of 5.\\
Removing duplicate blocks changed 1 method.\\
The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 47 to 39 Line Volume. This did not influence the risk category of this method, it is still high risk.\\
\\
Token Volume\\
Created a new method with a low risk Token Volume of 30.\\
Removing duplicate blocks changed 1 method.\\
The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 303 to 271 Token Volume. This increased the risk category of this method from high to moderate.\\
\\
The new method has a low risk Unit Interface Size of 1.\\
\\
Duplication went from 2.66\% to 2.63\%. This did not influence the risk category of the duplication in this codebase, it is still low risk.
\end{quote}

@@

\subsection{Threats to Validity}
To limit the scope of this research, we chose not to include human subjects in this study. However, we think that the results of this study could be strengthened by performing a survey on software engineering practitioners. We have determined maintainability scores only based on literature input and statistical analysis. It would be valuable to have a control group rate the refactorings performed by CR, as an extra form of input regarding the quality of the code transformations that CR performs.

In Section~\ref{sec:metricformula} we proposed an aggregation to measure a maintainability score on small-grained changes. The assumptions stated in this section influence the validity of the maintainability scores shown in our results. We noticed that the maintainability scores displayed in Table~\ref{tab:relation_refactor} and Table~\ref{tab:return} were mostly influenced by the differences in the ``number of parameters'' metric. This is because, for the scores, we normalized the metrics over all values obtained by these metrics. As our data regarding ``number of parameters'' has a very low standard deviation, small changes in this metric will influence the maintainability score a lot.
